\papertitle

### 2012-10-13 manuscript.tex
Various fixes based on Ron's feedback.

We demonstrate the performance of the location estimation and navigation 
algorithms. We model the backwards-reachable region for successfully 
navigating through narrow openings. Finally, we verify this model through 
with collected in experiments with narrow passage traversal.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ACM METADATA

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%TODO ryan
\begin{figure}[!tb]
\centering
\includegraphics[width=\linewidth]{figures/h2bird.png}
\caption{H$^2$Bird ornithopter MAV}
\label{fig:h2bird}
\end{figure}
The power, size, and weight constraints of micro air vehicle (MAV) 
platforms significantly limit on-board sensing and computational 
resources, and thus the complexity of the control and state estimation 
algorithms which can be executed on-board. These constraints are 
particularly severe for flapping wing MAVs, a class of MAVs that have inherently superior 
safety, efficiency, and noise profile to rotor craft MAVs, but at the 
expense of payload weight.
%Intro portion about previous works in ornithopter coorperative control/
%modeling ( won't necessarily stay in this spot)
Modeling and control of flapping wing MAVs is a well studied subject. 
Shigeoka discusses velocity and altitude control in
~\cite{Shigeoka:ornithopter}. In~\cite{delfly:design} deCroon et al. %TODO sentence fragment
In contrast, there is little previous work on guidance of flapping wing 
MAVs. Baek demonstrated altitude control with an external 
camera~\cite{baek:altitude}. de Croon et al. demonstrated obstacle avoidance 
with an onboard camera and offboard processing~\cite{delfly:avoid}. 
%[However, these papers do not study the system blah blah blah.]

@@

Attitude estimation and control for the H$^2$Bird runs on-board to achieve 
maintain high-rate attitude control. We estimate the vehicle pose by naively
integrating the IMU, and use PID for controlling the vehicle.

The high pitch angles H$^2$Bird achieves in routine flight distinguishes it 
from other MAVs. Baek 
demonstrated control on a similar vehicle using PID and an Euler angle
parameterization of orientation~\cite{baek:tracking}. However, Euler angle parameterizations of the vehicle orientation 
suffer from singularities around these high pitch angles, so we instead 
represent the vehicle orientation with quaternions. An additional benefit of 
the quaternion representation its ability to represent relative body and 
world coordinate angular displacements compactly with quaternion 
multiplication.

@@

We tested our cooperative visual servoing system with a simple target seeking
experiment: the H$^2$Bird must fly through a specified obstacle, in this case,
a wooden frame meant to simulate a window. As the H$^2$Bird cannot detect the
target on its own,we used the ground station to provide remote headings for
navigation to the window. Ground truth data was collected via a motion capture
system in the test room. A sketch of the experimental setup is shown in
Fig.~\ref{fig:experiment_cartoon}.

@@

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/experiment_cartoon.pdf}
\caption{Conceptual sketch of experimental environment.}
\label{fig:experiment_cartoon}
\end{figure}
%TODO label experiment cartoon

>>>>

We demonstrate the performance of the location estimation and navigation 
algorithms. We model the backwards-reachable region for successfully 
navigating through narrow openings. Finally, we verify this model through 
with experiments with narrow passage traversal.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ACM METADATA

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%TODO ryan
\begin{figure}[!tb]
\centering
\includegraphics[width=\linewidth]{figures/h2bird.png}
\caption{H$^2$Bird ornithopter MAV}
\label{fig:h2bird}
\end{figure}
The power, size, and weight constraints of micro air vehicle (MAV) 
platforms significantly limit on-board sensing and computational 
resources, and thus the complexity of the control and state estimation 
algorithms which can be executed on-board. These constraints are 
particularly severe for flapping wing MAVs, a class of MAVs that have inherently superior 
safety, and noise profile to rotor craft MAVs, but at the 
expense of payload weight.
%Intro portion about previous works in ornithopter coorperative control/
%modeling ( won't necessarily stay in this spot)
Modeling and control of flapping wing MAVs is becominga well studied subject. 
Shigeoka discusses velocity and altitude control in
~\cite{Shigeoka:ornithopter}. Design and control of the sub 15 gram DelFly
ornithopter is described by deCroon et al.~\cite{delfly:design}.
In contrast, there is little previous work on guidance of flapping wing 
MAVs. Baek demonstrated altitude control with an external 
camera~\cite{baek:altitude}. de Croon et al. demonstrated obstacle avoidance 
with an onboard camera and offboard processing~\cite{delfly:avoid}. For sub 20 gram
ornithopters, Baek et al. \cite{baek:tracking} is one of the few examples of
completely autonomous target seeking.
%[However, these papers do not study the system blah blah blah.]

@@

Attitude estimation and control for the H$^2$Bird runs on-board to achieve 
maintain high-sample-rate attitude control. We estimate the vehicle pose by naively
integrating the IMU, and use a proportional plus integral plus derivative (PID) 
controller for controlling the vehicle.

The high pitch angles flapping wing flyers achieve in routine flight distinguish them 
from other MAVs. Baek demonstrated control on a similar vehicle using PID and an Euler angle
parameterization of orientation~\cite{baek:tracking}. However, Euler angle parameterizations of the vehicle orientation 
suffer from singularities around these high pitch angles, so we instead 
represent the vehicle orientation with quaternions. An additional benefit of 
the quaternion representation is its ability to represent relative body and 
world coordinate angular displacements compactly with quaternion 
multiplication.

@@

We tested our cooperative visual servoing system with a simple target seeking
experiment: the H$^2$Bird must fly through a specified obstacle, in this case,
a wooden frame meant to simulate a window. As the H$^2$Bird cannot detect the
target on its own, we used the ground station to provide remote headings for
navigation to the window. Ground truth data was collected via a motion capture
system in the test room. A sketch of the experimental setup is shown in
Fig.~\ref{fig:experiment_cartoon}.

@@

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/experiment_cartoon.pdf}
\caption{Conceptual sketch of experimental setup.}
\label{fig:experiment_cartoon}
\end{figure}
%TODO label experiment cartoon
